cell-type-consensus Analysis

### 2024-11-19 analyses/cell-type-consensus/notebook-template.Rmd
initiate consensus module

---
title: "cell-type-nonETP-ALL-03 Analysis"
author:
  - Your name here
date: "`r Sys.Date()`"
output: html_notebook
---

@@

# The path to this module
module_base <- file.path(repository_base, "analyses", "cell-type-nonETP-ALL-03")
```

>>>>

---
title: "cell-type-consensus Analysis"
author:
  - Your name here
date: "`r Sys.Date()`"
output: html_notebook
---

@@

# The path to this module
module_base <- file.path(repository_base, "analyses", "cell-type-consensus")
```
